Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-04-22 paper.tex
Abstract says 'problematic' instead of 'difficult'

% ========
% Abstract
% ========
\begin{abstract}
Rendering intersecting volumes is difficult because the renderer must alternate
between sampling from each volume to achieve the correct blending.  Methods for
rendering an arbitrary number of intersecting volumes on the GPU have been
developed, but they can require a large amount of geometry to be created every
frame, or may be difficult or time-consuming to implement.  This paper
investigates whether using familiar Boolean operations may be faster or easy to
implement in the simple case where two axis-aligned volumes intersect.
\end{abstract}

>>>>

% ========
% Abstract
% ========
\begin{abstract}
Rendering intersecting volumes is problematic because the renderer must
alternate between sampling from each volume to achieve the correct blending.
Methods for rendering an arbitrary number of intersecting volumes on the GPU
have been developed, but they can require a large amount of geometry to be
created every frame, or may be difficult or time-consuming to implement.  This
paper investigates whether using familiar Boolean operations may be faster or
easy to implement in the simple case where two axis-aligned volumes intersect.
\end{abstract}
